% =====================================================================
%  chapters/05_authorship.tex  --  DECLARATION OF AUTHORSHIP
% ---------------------------------------------------------------------
%  Official wording (LBS v6.1, §3.10). The pronouns switch automatically
%  between singular and plural based on \ifplural in config.tex.
%  Do not alter the declared text; only set the place/date and name in
%  config.tex and sign the printed copy by hand.
% =====================================================================
\addchap{Declaration of Authorship}

\textbf{\thetitle}\\
\ifshowsubtitle\textbf{\thesubtitle}\\\fi

\vspace{0.5em}

\ifplural
We hereby declare that the present paper is entirely our own work and
without the use of any unauthorised assistance. Any content which has
been taken verbatim or paraphrased from other sources has been
identified as such. We have named all the AI tools used with their
product names and described how they have been used in the list of aids.
We are aware that the use of machine-generated texts does not guarantee
the quality of content and text. We assure that we have only used AI
tools as an aid and that our creative influence predominates in this
work. We are fully responsible for the adoption of any machine-generated
text passages or other elements of the work. The insurance of
independent work also applies to included drawings, sketches or graphic
representations. This paper has not been submitted in any form
whatsoever to an examining body nor has it been published. By submitting
the electronic version of the final version of the thesis, we
acknowledge that it can be checked for plagiarism with the help of a
plagiarism detection service.
\else
I hereby declare that the present paper is entirely my own work and
without the use of any unauthorised assistance. Any content which has
been taken verbatim or paraphrased from other sources has been
identified as such. I have named all the AI tools used with their
product names and described how they have been used in the list of aids.
I am aware that the use of machine-generated texts does not guarantee
the quality of content and text. I assure that I have only used AI tools
as an aid and that my creative influence predominates in this work. I am
fully responsible for the adoption of any machine-generated text
passages or other elements of the work. The insurance of independent
work also applies to included drawings, sketches or graphic
representations. This paper has not been submitted in any form
whatsoever to an examining body nor has it been published. By submitting
the electronic version of the final version of the thesis, I acknowledge
that it can be checked for plagiarism with the help of a plagiarism
detection service.
\fi

\vspace{2cm}

% --- Place/date  |  Name --------------------------------------------
\noindent
\begin{minipage}[t]{0.45\textwidth}
  \centering\small \placedate \par
  \rule{\linewidth}{0.4pt}\par
  \small Place and date
\end{minipage}\hfill
\begin{minipage}[t]{0.45\textwidth}
  \centering\small \mainauthor \par
  \rule{\linewidth}{0.4pt}\par
  \small First name and last name
\end{minipage}

\vspace{2.5cm}

% --- Signature (right) ----------------------------------------------
\noindent
\begin{minipage}[t]{0.45\textwidth}\mbox{}\end{minipage}\hfill
\begin{minipage}[t]{0.45\textwidth}
  \centering \rule{\linewidth}{0.4pt}\par
  \small Signature
\end{minipage}
